---
title: "VRecruit"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: default
    storyboard: true
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(readr)
library(dplyr)
library(shiny)
library(digest)
library(plotly)
library(ggmap)
library(DT)
library(knitr)

#read in data
kolbe<- read_csv("/Users/em429g/Desktop/VR Recruit App/vrecruit_kolbe.csv")
```

Overall Dashboard {data-orientation=rows data-icon="fa-bar-chart"}
============================================================

## Row 1 {data-height=110}

### Active Candidates

```{r}
valueBox(20, icon = "fa-user-check", color="mediumseagreen")
```

### Scheduled Interviews
```{r}
valueBox(3, icon = "fa-spinner")
```

### New Game Assessments
```{r}
valueBox(2, icon = "fa-gamepad", color="tomato")
```

## Row 2 {data-height=400} 

### Game Session Length per Candidate

```{r}
x <- kolbe$candidate_name
y <- kolbe$session_length_sec

bar_chart_data <- data.frame(x, y)

#bar chart
p <- plot_ly(bar_chart_data, x = ~x, y = ~y, type = 'bar', color = I("#20B2AA")) %>%
  layout(title = "",
         xaxis = list(title = ""),
         yaxis = list(title = "seconds"))
p
```

### Average Kolbe Scores for Each Job Title
```{r}
k1<-c("Fact Finder", "Follow Through", "Quick Start", "Implementor")
de<-c(2, 3.6, 4, 6)
ds<-c(4, 4.3, 4.5, 4.5)
me<-c(4.5, 6.5, 4.5, 5.5)
pm<-c(5.3, 5.6, 3, 3.6)
se<-c(4.6, 5, 3.8, 3.6)
k2<-c(mean(kolbe$fact_finder), mean(kolbe$follow_thru), mean(kolbe$quick_start), mean(kolbe$implementor))
df3<-data.frame(k1,de,ds,me,pm,se,k2)

p3<- plot_ly(df3, x = ~k1, y = ~de, type = 'bar', name = 'Data Engineer', marker = list(color = '#6495ED')) %>%
  add_trace(y = ~ds, name = 'Data Scientist', marker = list(color = '#00BFFF')) %>%
  add_trace(y = ~me, name = 'Mechanical Engineer', marker = list(color = '#1E90FF')) %>%
  add_trace(y = ~pm, name = 'Project Manager', marker = list(color = '#ADD8E6')) %>%
  add_trace(y = ~se, name = 'Software Engineer', marker = list(color = '#87CEEB')) %>%
  layout(xaxis = list(title = "", tickangle = -45),
         yaxis = list(title = ""),
         margin = list(b = 100),
         barmode = 'group')

p3
```

Candidate Profile {data-orientation=rows}
============================================================

## Row 1 {data-height=40}

### Candidate #17
```{r}
valueBox("Kris Kornell", icon = "fa-user-circle", color="tomato")
```

## Row 2 {data-height=40}

### Interview Process Complete
```{r}
valueBox("80%", icon = "fa-spinner")
```

### Open Job Applications
```{r}
valueBox(2, icon = "fa-folder-open", color="mediumseagreen")
```

## Row {data-height=150}

### Kolbe Test Assessment
```{r}
#radar chart
p4 <- plot_ly(
    type = 'scatterpolar',
    fill='toself'
  ) %>%
  add_trace(
    r = c(7, 7, 3, 8),
    theta = c('Fact Finder','Follow Through','Quick Start', 'Implementor'),
    name = 'Candidate Assessment'
  ) %>%
  add_trace(
    r = c(4.15, 4.85, 3.9, 4.45),
    theta = c('Fact Finder','Follow Through','Quick Start', 'Implementor'),
    name = 'Average Assessment'
  ) %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(0,10)
      )
    )
  )

p4
```

### Ideal Job Placement based on Kolbe Assessment

```{r}
y <- c('Fact Finder<br>STRATEGIZE',
       'Follow Through<br>SYSTEMATIZE',
       'Quick Start<br>STABILIZE',
       'Implementor<br>PROTECT')
x1 <- c(21, 24, 27, 29)
x2 <-c(30, 31, 26, 24)
x3 <- c(21, 19, 23, 15)
x4 <- c(16, 15, 11, 18)
x5 <- c(12, 11, 13, 14)

data <- data.frame(y, x1, x2, x3, x4, x5)

top_labels <- c('Software<br>Engineer', 'Data<br>Scientist', 'Project<br>Manager', 'Mechanical<br>Engineer', 'Data<br>Engineer')

p5 <- plot_ly(data, x = ~x1, y = ~y, type = 'bar', orientation = 'h',
        marker = list(color = 'rgba(102,205,170, 0.8)',
                      line = list(color = 'rgba(0, 0, 0, 0)', width = 1))) %>%
  add_trace(x = ~x2, marker = list(color = 'rgba(91,184,153, 0.8)')) %>%
  add_trace(x = ~x3, marker = list(color = 'rgba(72,147,122, 0.8)')) %>%
  add_trace(x = ~x4, marker = list(color = 'rgba(50,102,85, 0.8)')) %>%
  add_trace(x = ~x5, marker = list(color = 'rgba(30,61,51, 0.8)')) %>%
  layout(xaxis = list(title = "",
                      showgrid = FALSE,
                      showline = FALSE,
                      showticklabels = FALSE,
                      zeroline = FALSE,
                      domain = c(0.15, 1)),
         yaxis = list(title = "",
                      showgrid = FALSE,
                      showline = FALSE,
                      showticklabels = FALSE,
                      zeroline = FALSE),
         barmode = 'stack',
         paper_bgcolor = 'rgba(0, 0, 0, 0)', plot_bgcolor = 'rgba(0, 0, 0, 0)',
         margin = list(l = 120, r = 10, t = 140, b = 80),
         showlegend = FALSE) %>%
  # labeling the y-axis
  add_annotations(xref = 'paper', yref = 'y', x = 0.14, y = y,
                  xanchor = 'right',
                  text = y,
                  font = list(family = 'Arial', size = 12,
                            color = 'rgb(67, 67, 67)'),
                  showarrow = FALSE, align = 'right') %>%
  # labeling the percentages of each bar (x_axis)
  add_annotations(xref = 'x', yref = 'y',
                  x = x1 / 2, y = y,
                  text = paste(data[,"x1"], '%'),
                  font = list(family = 'Arial', size = 12,
                            color = 'rgb(248, 248, 255)'),
                  showarrow = FALSE) %>%
  add_annotations(xref = 'x', yref = 'y',
                  x = x1 + x2 / 2, y = y,
                  text = paste(data[,"x2"], '%'),
                  font = list(family = 'Arial', size = 12,
                              color = 'rgb(248, 248, 255)'),
                  showarrow = FALSE) %>%
  add_annotations(xref = 'x', yref = 'y',
                  x = x1 + x2 + x3 / 2, y = y,
                  text = paste(data[,"x3"], '%'),
                  font = list(family = 'Arial', size = 12,
                              color = 'rgb(248, 248, 255)'),
                  showarrow = FALSE) %>%
  add_annotations(xref = 'x', yref = 'y',
                  x = x1 + x2 + x3 + x4 / 2, y = y,
                  text = paste(data[,"x4"], '%'),
                  font = list(family = 'Arial', size = 12,
                              color = 'rgb(248, 248, 255)'),
                  showarrow = FALSE) %>%
  add_annotations(xref = 'x', yref = 'y',
                  x = x1 + x2 + x3 + x4 + x5 / 2, y = y,
                  text = paste(data[,"x5"], '%'),
                  font = list(family = 'Arial', size = 12,
                              color = 'rgb(248, 248, 255)'),
                  showarrow = FALSE) %>%
  # labeling the first Likert scale (on the top)
  add_annotations(xref = 'x', yref = 'paper',
                  x = c(21 / 2, 21 + 30 / 2, 21 + 30 + 21 / 2, 21 + 30 + 21 + 16 / 2,
                        21 + 30 + 21 + 16 + 12 / 2),
                  y = 1.15,
                  text = top_labels,
                  font = list(family = 'Arial', size = 12,
                              color = 'rgb(67, 67, 67)'),
                  showarrow = FALSE)
p5
```

